%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{fontspec}
\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Calluna}
\linespread{1.13}
\setmonofont[Scale=.95]{Inconsolata}
\usepackage{hyperref}
\usepackage{xunicode}

% Footnotes to the bottom of the page
\usepackage[bottom]{footmisc}
\renewcommand*{\footnotelayout}{\small\sffamily}
\renewcommand{\footnoterule}{
  \kern -3pt
  \hrule width 3cm height .5pt \color{grey }
  \kern 5pt
 
}

\pagestyle{empty}


% Margins
\usepackage{geometry} 
\geometry{a4paper, textwidth=4.8in, textheight=9.5in, marginparsep=20pt, marginparwidth=2in}
\renewcommand\footnotelayout{\fontsize{10}{-50}\selectfont}
% \urlstyle{same}

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{} 

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\signature{Antonio Piu} % Your name for the signature at the bottom

\makeatletter
\renewcommand{\closing}[1]{\par\nobreak\vspace{\parskip}%
  \stopbreaks
  \noindent
  \ifx\@empty\fromaddress\else
  \hspace*{\longindentation}\fi
  \parbox{\indentedwidth}{\raggedright
       \ignorespaces #1\\[0\medskipamount]%
       \ifx\@empty\fromsig
           \fromname
       \else \fromsig \fi\strut}%
   \par}
\makeatother

\makeatletter
\renewcommand*{\opening}[1]{%
%  \ifx\@empty\fromaddress
%    \thispagestyle{firstpage}%
%      {\raggedleft\@date\par}%
%  \else  % home address
%    \thispagestyle{empty}%
%    {\raggedleft\begin{tabular}{l@{}}\ignorespaces
%      \fromaddress \\*[2\parskip]%
%      \@date \end{tabular}\par}%
%  \fi
%  \vspace{2\parskip}%
%  {\raggedright \toname \\ \toaddress \par}%
  \begin{minipage}[t]{0.5\textwidth}%
    \toname \\ 
    \toaddress
  \end{minipage}\hfill\@date\par
  \vspace{1.5\parskip}%
  #1\par\nobreak}
\makeatother

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Mr. Fabian Wunderlich,\\}

I am writing for the position of \textbf{Senior Product/Web Designer}, found in the website \emph{http://berlinstartupjobs.com/}. I believe my knowledge and experience is appropriate for this position, and I would like to apply.

I am from Italy. I would be willing to move to Germany and start working as soon as required. 

I left my last position at Net7 in April 2012, and began working as a Freelance designer.
The work showcased on my portfolio\footnote{\url{http://antoniopiu.com}} is the track record of the \emph{2012-2013} activity and the projects have been selected from my freelance experience only, so it is possible to easily evaluate the quality and the variety of the design.

Recently I worked as a Web Designer for Turini Group\footnote{\url{http://turinigroup.com/en}}, a well-known italian Law firm, to renew their corporate website network and redesign two of their online services: \emph{Patent Office}\footnote{\url{http://antoniopiu.com/works/ufficiobrevetti}} (focusing the efforts on mobile interface usability) and Brevettinews\footnote{\url{http://antoniopiu.com/works/brevettinews}} (which has been a readability and marketing challenge as I renewed the entire online presence—including the magazine logo and the newsletter design). 

I have over eight years of experience as a web designer. I use to code the designs I make, using \textsc{html/css/sass}. I also use Git. I am recently learning more about \textsc{ux} and interaction design. I love photography and typography and I think my multidisciplinary experience can be a good contribution for this project.

I had been learning German for five years during high school. Still, I can not say I am not professionally proficient speaking German yet as time passed since my intensive language camp in Germany. Anyway I'd like to take courses as soon as I relocate. I also speak fluent Spanish, basic French.

If you find my profile interesting, please get in touch. I am also available
for a call on Skype: my username is \emph{puleddu}.

Thank you very much for taking the time to consider my credentials.

\closing{Sincerely,}
\end{letter}
\end{document}